Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-05-29 WRITEUP/ms.tex
minor edits

@@

\begin{abstract}
%mm rearranged sentence
We study the properties of molecular cloud complexes (MCCs) using cosmological zoom-in simulation of a
$z\simeq 6$ prototypical galaxy (``\flower'').
%
We identify MCCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter 
to \obs.
%
In \flower, MCC masses are in the range of $10^{5.5-8.5}$\,\Msun, with sizes $R\lesssim200$\,pc. 
% 
We identify gravitationally unstable MCCs both via Toomre $Q_{\rm eff}$ analysis and
the more observationally accessible virial parameter ($\alpha_{\rm vir}$) analysis. 
MCCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
instability to % gravitational 
collapse.
%
Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
% 
We show that large-scale rotation is an important contributor to the velocity dispersion of MCCs, even in the highly disturbed phase of \flower, posing 
a challenge to the interpretation of molecular gas dynamics in \highz galaxies in the literature.
% Thus, velocity dispersions measured on similar scales (even down to 40\,pc) should not be taken as a direct 
% evidence that \highz molecular gas are intrinsically more turbulent than the local ISM, 
% unless contributions from bulk motions are properly accounted for.
% 
%Close resemblance of $Q_{\rm eff}$ and $Q_{\star}$ maps illustrates the importance of accounting for stellar contribution and disk thickness when 
%examining the stability of molecular gas structures, especially in relatively evolved and enriched systems at high redshift 
%that are preferentially being observed now.
% 
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) on
$\lesssim$40\,pc are necessary to shed light on the star-forming gas dynamics since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

%mm rearranged and combined this and the following paragraph to proceed from observation to conclusion
Early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population.
%
As a consequence, we expect them to be significantly more ionized, and have intense and hard interstelar radiation fields (ISRF). Since their metallicity and dust content are also expected to be lower in these early evolutionary stages, shielding of UV photons---responsible for the photoheating of the gas---  is strongly reduced. Such differences in turn affect the regulation of the thermal and chemical state of the multi-phase interstellar medium (ISM). Studying ISM properties of early galaxies is essential for understanding how \SF proceeds under more extreme conditions.
%
Even in the local Universe, where detailed \obs can be made, variations in molecular cloud
%       \MM{do Hughes et al. study cloud complexes, as you do, or can you derive info about complexes from their data?}
%     \DL{This is just a statement to say there are variations among local GMCs. Together with the different galaxy properties found for early galaxies, it is interesting to study properties of molecular structures at earlier epochs. }
properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).  Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of
molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop?}
%

@@

In cases where stellar component plays an important role in the dynamics, the virial parameter becomes
\begin{equation}
\alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm gas} + M_{\star})} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
					       {M_{\rm gas} + M_{\star} }\,,
\label{eqn:alpha_tot}
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
\DL{Should we leave out $\sigma_{\star}$ since stellar motions shouldn't affect the gas?}

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The full velocity dispersion of MCCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
\begin{equation}
\sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas. Therefore, when calculating global quantities for MCS, we always perform a mass-weighting. Since we operate on data on a unigrid, this is equivalent to density averaged quantities. In general, for the quantity $x$ in a MCC we write
\begin{equation}\label{eqn:defineaverage}
\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells indexed by $i$ composing the MCC. We can use the defintion \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
%
The bulk velocity dispersion is
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
\end{equation}
%
The thermal sound speed is calculated from the thermal pressure ($P_{\rm TH}$) through
\begin{equation}
c_s^2 = \left\langle \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right\rangle\,,
\end{equation}
where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton. Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
\begin{equation}
\sigma_{\rm NT}^2 = \left\langle \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n}\right\rangle\,.
\end{equation}
%
Finally, the Mach number is related to the pressure terms as follows
\begin{equation}
\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
\label{eqn:MPress}
\end{equation}

@@

We start by considering the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We show in \Fig{dist} the results for the distributions considering all the evolutionary stages and dividing the sample in a low ($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm cut}$\eq18.96\,\cc, lower panels) density cuts\footnote{The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure. However, not all evolutionary stages considered have at least one MCC at this highest density threshold, we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc).}.
%
Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}. The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower.
%
The most massive ($M_{\rm gas}>$10$^8$\,\Msun) cloud identified at each density threshold corresponds to the molecular disk of the galaxy, which is identified as a single component for low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16} has a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio of $\simeq$\,50--100.

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower.
The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} as they correspond to a large part of \flower, and thus,
include a large number of stellar mass already ensembled in \flower 
\label{fig:stellarRatio16}}
\end{figure}

@@

The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$. In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
%
This can be further analyzed as follows. In \Fig{vv} we show the gas velocity dispersions from bulk motions versus turbulent motions for MCCs in the accreting and quiescent phase. Recall that \flower displays a disturbed morphology in the accreting phase but a disk-like morphology in the quiescent phase (see \Fig{MCC} and \Fig{MCC28}).
%
Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions, whereas the opposite is true in the quiescent phase. In addition, the two velocity dispersion terms are of the same order of magnitude.
% as the two are connected via the Euler equation
\AP{I still do not get the point; bulk motion is a dispersion, i.e. should not receive contribution from the rotation of the system; a possibility might be to calulate the specific angular momentum ($\vec{x}\wedge\vec{v}$ averaged using \Eq{defineaverage}) of the system and compare it to the one for gas in circular motion} {\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here have an important contribution from large-scale rotation.}
%
Hence, the linewidths observed in \highz molecular gas structures on these scales should {\em not} be taken as a direct evidence they are intrinsically more turbulent than those in the local ISM, and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial. \citet{Behrendt16a} draw a similar conclusion using pc-scale resolution simulation: large-scale bulk motions may mimic turbulent velocity dispersion due to beam smearing, even though contributions due to self-rotation of each individual sub-MCCs is washed out within the beam \AP{they argue that self-rotation is not important, but i do not see how we match the result with our analysis}.

\AP{I would not remove the mass-size relation discussion (commented now in the text)}

@@

\AP{Q was introduced at page 3, but then not used. I think some intro sentence should be added here}
Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Qeff} (see also \Fig{h2density} for example of MCCs identified in this evolutionary stage of \flower using different $n_{\rm cut}$).

Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against \AP{should we introduce this classification of the perturbations in the \Sec{Q}} $m$\eq0 perturbations. This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability. Similarly, contribution from the thickness of the disk is important in \flower since its disk is warped and has a scale height-to-radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.

That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, which is consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the thickness of its disk (via $\sigma_z$, see Equation~\ref{eqn:q_eff}), some of these MCCs are consistent with $Q_{\rm eff} > 1$.
%
This demonstrates the importance of accounting for stellar contribution and disk thickness when examining the stability of molecular gas structures. This consideration is especially relevant for the relatively evolved and enriched systems at high redshift, that are preferentially being imaged at high resolution with ALMA. In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. Notably, these are the more gas-rich regions (see \Fig{sigma}).

The large virial parameters seen in some MCCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution/collapse depends on the dynamics or equation of state of the gas.
%
Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$. Second, this fragmentation scale is greater than the typical size of GMCs.
%
This could be interpreted as a result of instability setting the scales for fragmentation, {\em but the truly star-forming regions correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales}.
%
Thus, \AP{from the sentence, it is unclear if the Q analysis is consistent or is in an independent indication with respect to the virial parameter analysis} the high virial parameter found for some MCCs in \flower indicates that they are not the collapsing structures (but the virial parameter varies depending on the evolutionary stage of \flower) and are found in regions of $Q_{\rm eff}>1$. On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.

@@

MCCs of \flower are found to have velocity dispersion and gas surface density systematically higher than
Milky Way clouds regardless of the density threshold $n_{\rm cut}$ adopted.
These MCCs are, in fact, highly supersonic (with high Mach numbers).
Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma_{\rm gas}\simeq200$\,\kms); however,
comparing the velocity dispersions of MCCs from bulk motions versus turbulence
indicates that large-scale rotation is an important contributor, even in the
accreting phase of \flower, which displays a highly disturbed morphology.
This poses a challenge to the interpretation of spatially resolved molecular gas structures observed in \highz galaxies to-date.
In particular, any velocity dispersions measured on similar scales as here (even down to $\sim$\,40\,pc)
should {\em not} be taken as a direct evidence that \highz molecular gas structures are intrinsically more turbulent than those in the local ISM,
unless contributions from bulk motions are properly accounted for.
%This means that a lot of the velocity dispersion infer on even the few-tens of parsec scales have a non-negligible contribution
%from rotation (cf. solely random motion). Therefore it is not fair to say that \highz molecular gas ``clumps`` (or whatever name used
%for structures in the literature) are more turbulent based on solely measured velocity dispersion.

@@

\section*{Acknowledgements}
We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Jens for useful discussions.
%
TKDL acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
%
AF acknowledges support from the ERC Advanced Grant INTERSTELLAR
H2020/740120.
%mm
    M-MML acknowledges partial support by the NSF through award
    AST18-15461, and hospitality from the Insitute for Theoretical
    Astrophysics at the University of Heidleberg.
%
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA) held at the Center for Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli Foundation and the Simons Foundation.
%
We thank the KSPA Scientific and Local Organizing Committees, and the program founder, Pascale Garaud, for supporting the genesis of this work.
%
We also thank the Center for Cosmology and Particle Physics at the New York University for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
%
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
We acknowledge use of the Python programming language \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{Pymses} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk11a}.
%
%and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.

>>>>

% TO edit:
% alpha lesssim 2 MCCs are bounded. For reference, GMCs in MW and nearby galaxies: 0.1 - 10 \citep{Solomon87a, Bolatto08a, Heyer09a, Roman-Duval10a, Wong11a}

@@

\begin{abstract}
We study the properties of molecular cloud complexes (MCCs) using cosmological zoom-in simulation of a
$z\simeq 6$ prototypical galaxy (``\flower'').
%
We identify MCCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter
to \obs.
%
In \flower, MCC masses are in the range of $10^{5.5-8.5}$\,\Msun, with sizes $R\lesssim200$\,pc.
%
We identify gravitationally unstable MCCs both via Toomre $Q_{\rm eff}$ analysis and
the more observationally accessible virial parameter ($\alpha_{\rm vir}$) analysis.
MCCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
instability to % gravitational
collapse.
%
Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We show that large-scale rotation is an important contributor to the velocity dispersion of some MCCs, even in the highly disturbed phase of \flower.
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) on
$\lesssim$40\,pc are necessary to shed light on the star-forming gas dynamics since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

%mm rearranged and combined this and the following paragraph to proceed from observation to conclusion
Early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population \citep[see also a review by][]{Stark16a}.
%
As a consequence, we expect them to be significantly more ionized, and have intense and hard interstelar radiation fields (ISRF). Since their metallicity and dust content are also expected to be lower in these early evolutionary stages, shielding of UV photons---responsible for the photoheating of the gas---  is strongly reduced. Such differences in turn affect the regulation of the thermal and chemical state of the multi-phase interstellar medium (ISM). Studying ISM properties of early galaxies is essential for understanding how \SF proceeds under more extreme conditions.
%
Even in the local Universe, where detailed \obs can be made, variations in molecular cloud
%       \MM{do Hughes et al. study cloud complexes, as you do, or can you derive info about complexes from their data?}
%     \DL{This is just a statement to say there are variations among local GMCs. Together with the different galaxy properties found for early galaxies, it is interesting to study properties of molecular structures at earlier epochs. }
properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).  Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of
molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop?}
%

@@

In cases where stellar component plays an important role in the dynamics, the virial parameter becomes
\begin{equation}
\alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm gas} + M_{\star})} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
					       {M_{\rm gas} + M_{\star} }\,,
\label{eqn:alpha_tot}
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The full velocity dispersion of MCCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
\begin{equation}
\sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
% First term: large scale motion
% second and last terms: small scale
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas. Therefore, when calculating global quantities for MCS, we always perform a mass-weighting. Since we operate on data on a uni-grid, this is equivalent to density averaged quantities. In general, for the quantity $x$ in a MCC we write
\begin{equation}\label{eqn:defineaverage}
\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells indexed by $i$ composing the MCC. We can use the definition \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
%
The bulk velocity dispersion is
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
\end{equation}
%
The thermal sound speed is calculated from the thermal pressure ($P_{\rm TH}$) through
\begin{equation}
c_s^2 = \left\langle \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right\rangle\,,
\end{equation}
where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton. Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
\begin{equation}
\sigma_{\rm NT}^2 = \left\langle \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n}\right\rangle\,.
\end{equation}
%
Finally, the Mach number is related to the pressure terms as follows
\begin{equation}
\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
\label{eqn:MPress}
\end{equation}

@@

We start by considering the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We show in \Fig{dist} the results for the distributions considering all the evolutionary stages and dividing the sample in a low ($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm cut}$\eq18.96\,\cc, lower panels) density cuts\footnote{The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure. However, not all evolutionary stages considered have at least one MCC at this highest density threshold, we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc).}.
%
Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}. The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower.
% GMCs in nearby galaxies: 10^5 < M < 1e7 Msun \citep{Rosolowsky03a, Freeman17a}
%
The most massive ($M_{\rm gas}>$10$^8$\,\Msun) cloud identified at each density threshold corresponds to the molecular disk of the galaxy, which is identified as a single component for low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16} has a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio of $\simeq$\,50--100.

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower.
The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} as they correspond to a large part of \flower, and thus,
include a large number of stellar mass that is already ensembled in \flower
\label{fig:stellarRatio16}}
\end{figure}

@@

The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$. In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
%
This can be further analyzed as follows. In \Fig{vv} we show the gas velocity dispersions from bulk motions versus turbulent motions for MCCs in the accreting and quiescent phase. Recall that \flower displays a disturbed morphology in the accreting phase but a disk-like morphology in the quiescent phase (see \Fig{MCC} and \Fig{MCC28}).
%
Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions, whereas the opposite is true in the quiescent phase. In addition, the two velocity dispersion terms are of the same order of magnitude.
% as the two are connected via the Euler equation
\DL{interpretation To be revised ...}
{\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here have an important contribution from large-scale rotation.}....
%
Hence, the linewidths observed in \highz molecular gas structures on these scales should {\em not} be taken as a direct evidence they are intrinsically more turbulent than those in the local ISM, and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.
\citet{Behrendt16a} draw a similar conclusion using pc-scale resolution simulation: large-scale bulk motions may mimic turbulent velocity dispersion due to beam smearing.

@@

We define Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ in \Sec{Q}.
Maps of the corresponding Toomre $Q$ are shown in \Fig{Qeff}
(see also \Fig{h2density} for example of MCCs identified in this evolutionary stage of \flower using different $n_{\rm cut}$).

Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against perturbations. This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability. Similarly, contribution from the thickness of the disk is important in \flower since its disk is warped and has a scale height-to-radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.

That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, which is consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the thickness of its disk (via $\sigma_z$, i.e., $Q_{\rm eff}$; see Equation~\ref{eqn:q_eff}), some of these MCCs are consistent with $Q_{\rm eff} > 1$.
%
This demonstrates the importance of accounting for stellar contribution and disk thickness when examining the stability of molecular gas structures. This consideration is especially relevant for the relatively evolved and enriched systems at high redshift, that are preferentially being imaged at high resolution with ALMA. In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. Notably, these are the more gas-rich regions (see \Fig{sigma}).

The large virial parameters seen in some MCCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution/collapse depends on the dynamics or equation of state of the gas.
%
Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$. Second, this fragmentation scale is greater than the typical size of GMCs.
%
This could be interpreted as a result of instability setting the scales for fragmentation, {\em but the truly star-forming regions correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales}.
%
Thus, the high virial parameter found for some MCCs in \flower indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$. On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.

@@

MCCs of \flower are found to have velocity dispersion and gas surface density systematically higher than
Milky Way clouds regardless of the density threshold $n_{\rm cut}$ adopted.
These MCCs are, in fact, highly supersonic (with high Mach numbers).
Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma_{\rm gas}\simeq200$\,\kms);
\DL{TBD} however,
comparing the velocity dispersions of MCCs from bulk motions versus turbulence
indicates that large-scale rotation is an important contributor, even in the
accreting phase of \flower, which displays a highly disturbed morphology.
This poses a challenge to the interpretation of spatially resolved molecular gas structures observed in \highz galaxies to-date.
In particular, any velocity dispersions measured on similar scales as here (even down to $\sim$\,40\,pc)
should {\em not} be taken as a direct evidence that \highz molecular gas structures are intrinsically more turbulent than those in the local ISM,
unless contributions from bulk motions are properly accounted for.
%This means that a lot of the velocity dispersion infer on even the few-tens of parsec scales have a non-negligible contribution
%from rotation (cf. solely random motion). Therefore it is not fair to say that \highz molecular gas ``clumps`` (or whatever name used
%for structures in the literature) are more turbulent based on solely measured velocity dispersion.

@@

\section*{Acknowledgements}
We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Jens for useful discussions.
%
TKDL gratefully acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
%
AF acknowledges support from the ERC Advanced Grant INTERSTELLAR
H2020/740120.
% mm
M-MML acknowledges partial support by the NSF through award
AST18-15461, and hospitality from the Insitute for Theoretical
Astrophysics at the University of Heidleberg.
%
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA) held at the Center for Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli Foundation and the Simons Foundation.
%
We thank the KSPA Scientific and Local Organizing Committees, and the program founder, Pascale Garaud, for supporting the genesis of this work.
%
We also thank the Center for Cosmology and Particle Physics at the New York University for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
%
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
We acknowledge use of the Python programming language \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{Pymses} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk11a}.
%
%and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.
